Quantifying and partitioning uncertainties in retrievals of plant traits from imaging spectroscopy data

### 2021-03-05 manuscript/manuscript.tex
More formatting tweaks
Modify manuscript table to use actual values

\begin{table}
\caption{\label{tab:atmospheres} Globally-representative atmospheres used in this analysis.}
\centering
\begin{tabular}{lllll}
\hline
  Global relative abundance (\%)  & Surface elevation (m) & Aerosol optical depth & Water vapor (g cm$^{-2}$) & Profile type  \\
  \hline
  34.0 & 109 & 0.090 & 1.190 & Midlatitude summer \\
  13.8 & 105 & 0.123 & 2.716 & Midlatitude summer \\
  12.6 & 77 & 0.132 & 2.889 & Tropical \\
  9.1 & 1174 & 0.100 & 1.116 & Midlatitude summer \\
  8.7 & 263 & 0.350 & 1.748 & Midlatitude summer \\
  8.7 & 88 & 0.168 & 4.323 & Tropical \\
  5.5 & 233 & 0.445 & 2.936 & Tropical \\
  4.5 & 911 & 0.135 & 1.853 & Tropical \\
  2.4 & 227 & 0.802 & 2.611 & Tropical \\
  0.7 & 3571 & 0.138 & 0.543 & Midlatitude summer \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Size & Values & Comments \\
  \hline
  Atmosphere & 10 & \emph{See Table~\ref{tab:atmospheres}} & \\ 
  Constellation inter-calibration scale & 3 & 0, 16, 32 & \\
  Constellation atmospheric noise (\%) & 4 & 0, 1, 5, 10 & \\
  Constellation angular noise (\%) & 4 & 0, 1, 5, 10 & \\
  Local time (24H) & 10 & 9:30, 10:00, 10:15, 10:30, 10:45, 11, 12, 13:30, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Date & 7 & March 20, May 20, June 20, July 20, August 20, September 22, December 21 & Northern hemisphere equinoxes and solstices, as well as denser sampling in summer (when traits are typically mapped) \\
  Sensor zenith (degrees) & 6 & 0, 12.5, 25, 37.5, 50, 75  & \\
  Sensor relative azimuth (degrees) & 5 & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{3}{l}{21,000} \\
  \hline
\end{tabular}
\end{table}

>>>>

\begin{table}
\caption{\label{tab:atmospheres} Globally-representative atmospheres used in this analysis.}
\centering
\begin{tabular}{p{0.15\textwidth}p{0.15\textwidth}p{0.15\textwidth}p{0.15\textwidth}p{0.3\textwidth}}
\hline
  Global relative abundance (\%)  & Surface elevation (m) & Aerosol optical depth & Water vapor (g cm$^{-2}$) & Profile type  \\
  \hline
  34.0 & 109 & 0.090 & 1.190 & Midlatitude summer \\
  13.8 & 105 & 0.123 & 2.716 & Midlatitude summer \\
  12.6 & 77 & 0.132 & 2.889 & Tropical \\
  9.1 & 1174 & 0.100 & 1.116 & Midlatitude summer \\
  8.7 & 263 & 0.350 & 1.748 & Midlatitude summer \\
  8.7 & 88 & 0.168 & 4.323 & Tropical \\
  5.5 & 233 & 0.445 & 2.936 & Tropical \\
  4.5 & 911 & 0.135 & 1.853 & Tropical \\
  2.4 & 227 & 0.802 & 2.611 & Tropical \\
  0.7 & 3571 & 0.138 & 0.543 & Midlatitude summer \\
\hline
\end{tabular}
\end{table}

\begin{table}
\caption{\label{tab:combinations} Factorial combination of inputs}
\centering
\begin{tabular}{p{0.2\linewidth}lp{0.4\linewidth}p{0.3\linewidth}}
  \hline
  Variable & Values & Comments \\
  \hline
  Atmosphere & \emph{See Table~\ref{tab:atmospheres}} & \\
  Date & March 20, June 21, September 22, December 21 & Northern hemisphere equinoxes and solstices
  Local time (24H) & 9:30, 10:00, 10:30, 12, 15:00 & Spaced over the day, with denser sampling around typical ``A-train'' satellite overpass around 10:30AM \\
  Sensor zenith (degrees) & 0, 10, 30  & \\
  Sensor relative azimuth (degrees) & 0, 30, 60, 90, 180 & \\
  \hline
  Total grid size & \multicolumn{2}{l}{64,800} \\
  \hline
\end{tabular}
\end{table}
